PACE Solver Description: OCMu64,\\ a solver for One-sided Crossing Minimization

### 2024-09-20 tex/paper.tex
Minor changes to paper.tex.

\begin{remark}\label{rem:strongest}
    Suppose that $u, v$ with $\bar u \neq \bar v$ are not strongly fixed, and let $b \in A$ be
    such that $F_{\bar u}(b) < F_{\bar v}(b)$.
    We would like to construct a node $X\in B$ such that $c(v, X, u) < \min(c(X,
    u, v), c(u, v, X))$, so that $v\b u$.
    Suppose that there are nodes $l, m,
    r \in A$, with $m$ sitting between $b$ and its successor in $A$, and $l < (\supp(u) \cup
    \supp(v)) < r$. Then let $X$ be connected to $l, m, r$. By choosing
    the weights of $X$ appropriately, we can let both $r(X, v) = W_v r(X, \bar v)$ and $r(u, X)
    = W_u r(\bar u, X)$ grow arbitrarily large. Since we can scale up the weights of $X$, it
    suffices to make $r(X, \bar v)$ and $r(\bar u, X)$ simultaneously positive.

    Now $r(X, \bar v) = (2F_{\bar v}(b) - 1)X(m) + (X(r) - X(l))$, and $r(\bar u, X) = (1 -
    2F_{\bar u}(b))X(m) - (X(r) - X(l))$. By choosing the weights $X(r), X(l)$ appropriately, we can make
    these two values equal, so it suffices if their \emph{average} is positive, and indeed
    $${(r(X, \bar v) + r(\bar u, X))/2 = X(m)(F_{\bar v}(b) - F_{\bar u}(b)) > 0}.$$
    This implies $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, and thus
    demonstrates that if one wants to show that $u \b v$, when $u,
    v$ are not strongly fixed, one must consider features of the graph other than $u, v$ and
    their neighbours, so indeed \cref{lem:sfp} is optimal. Note that this also applies in the unweighted case,
    by taking $l, m, r$ to be sets of nodes rather than weighted single nodes.
\end{remark}

>>>>

\begin{remark}\label{rem:strongest}
    Suppose that $u, v$ with $\bar u \neq \bar v$ are not strongly fixed, and let $b \in A$ be
    such that $F_{\bar u}(b) < F_{\bar v}(b)$.
    We would like to construct a node $X\in B$ such that $c(v, X, u) < \min(c(X,
    u, v), c(u, v, X))$, so that $v\b u$.
    Suppose that there are nodes $l, m,
    r \in A$, with $m$ sitting between $b$ and its successor in $A$, and $l < (\supp(u) \cup
    \supp(v)) < r$ (see \cref{fig:blocking}). Then let $X$ be connected to $l, m, r$. By choosing
    the weights of $X$ appropriately, we can let both $r(X, v) = W_v r(X, \bar v)$ and $r(u, X)
    = W_u r(\bar u, X)$ grow arbitrarily large. Since we can scale up the weights of $X$, it
    suffices to make $r(X, \bar v)$ and $r(\bar u, X)$ simultaneously positive.

    Now $r(X, \bar v) = (2F_{\bar v}(b) - 1)X(m) + (X(r) - X(l))$, and $r(\bar u, X) = (1 -
    2F_{\bar u}(b))X(m) - (X(r) - X(l))$. By choosing the weights $X(r), X(l)$ appropriately, we can make
    these two values equal, so it suffices if their \emph{average} is positive, and indeed
    $${(r(X, \bar v) + r(\bar u, X))/2 = X(m)(F_{\bar v}(b) - F_{\bar u}(b)) > 0}.$$
    This implies $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, and thus
    demonstrates that if one wants to show that $u \b v$, when $u,
    v$ are not strongly fixed, one must consider features of the graph other than $u, v$ and
    their neighbours. In other words, \cref{lem:sfp} is optimal. Note that this remark also
    applies in the unweighted case, by taking $l, m, r$ to be sets of nodes rather than
    weighted single nodes.
\end{remark}
